---
title: "lab4"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{lab4}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(lab4)
```


# Overview
lab4 is a package to handle linear regression models. It can handle functions such as print(), plot(), resid(), pred(), coef() and summary().

# Import

```{r}
    library(lab4)
```

# Methods

The example below is to introduce how these functions work
`linreg()` takes two parameter, Form : formula; data :  a data.frame  

```{r}
linreg_mod <- linreg$new(Form = Petal.Length~Species, data=iris)
```

The `print()` prints out the vector containing coefficients.

```{r}
linreg_mod$print()
```

The `plot()`  plots such pictures(package ggplot2 is needed here)

```{r}
linreg_mod$plot()
```

The `resid()` returns the vector of residuals.

```{r}
head(linreg_mod$resid())
```

The `pred()` returns the predicted values.

```{r}
head(linreg_mod$pred())
```

The `coef()` returns the coefficients as a named vector.

```{r}
linreg_mod$coef()
```

The `summary()`  returns a similar printout as printed for lm objects, but you only need to present
the coefficients with their standard error, t-value and p-value as well as the estimate of ˆσ and the degrees
of freedom in the model.

```{r}
linreg_mod$summary()
```
